Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-05-20 article-models-ttinternal.tex
implementing code in text --- not working!

\begin{defn}
A term-algebra in context $\Gamma$ is a septuple 
$(A,P,T,\epsilon_0,\epsilon_1,\phi_0,\phi_1)$ such that the quadruple
$(A,P,\epsilon_0,\epsilon_1)$ is an extension algebra in context $\Gamma$, 
the quadruple $(A,P,\phi_0,\phi_1)$ is an empty algebra in context $\Gamma$,
for which we additionally have the following judgmental equality:
\begin{align*}
\jfameq*{{\Gamma}{A}}{\subst{\phi_1}{T}}{\emptyf}.
\end{align*}
\end{defn}

>>>>

\begin{defn}
A term-algebra $\cftalg{A}$ in context $\Gamma$ is a septuple 
\begin{equation*}
\unfold{\cftalg{A}}
\end{equation*}
such that the quadruple
$\unfold{\extalg{A}}$ is an extension algebra in context $\Gamma$, 
the quadruple $\unfold{\empalg{A}}$ is an empty algebra in context $\Gamma$,
for which we additionally have the following judgmental equality:
\begin{align*}
\jfameq*{{\Gamma}{\cftalgc{\cftalg{A}}}}{\subst{\cftempf{\cftalg{A}}}{\cftalgt{\cftalg{A}}}}{\emptyf}.
\end{align*}
\end{defn}
